---
title: "Homework 3"
author: "Data Science at StratCom, Spring 2019"
date: "Due on Mar 6, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache=TRUE)
```

  
1. Which plot do we generate to display relationship between 
    a. Two quantitative variables
    b. One quantitative and Categorical variable
    c. Two categorical variable
    d. One categorical vs many variables (regardless of type)

2. We have three variables X, Y, Z of which Y is response variable. What plot will show a two way interaction effect of X and Z on Y if
    a. one of them are quantitative and the other is categorical
    b. both of them are categorical
    c. both of them are quantitative
    
3. In class we presented how to reorganize data to display and generated a scatter plot of French fries data to show the relationship between replication 1 and 2. Generate and provide a similar plot that shows relationships between time 1 and 10 for each of the sensory attributes. Use any software including excel, if possible. The following `R` code will load `french_fries` data frame on R. You can save it as a CSV file to use on other software.
```{r}
library(reshape2)
head(french_fries)
```





